---
title: "Cereal Data Science Project"
author: "Eric Greiner"
date: "2022-09-29"
---
```{r}
library('tidyr')
library('tidyverse')

require('ggplot2')
require('tidyverse')
require('tidyr')
```

## Questions 

### Data Cleaning
 
1. Load the `cereal.csv` data 
```{r}
cereals = read_csv('cereals.csv')
```

```{r}
glimpse(cereals)
```
```{r}
head(cereals)
```

## Evaluate the "missingness" of the variables (i.e. what percent of each variable is complete)

```{r}
install.packages('skimr')
library('skimr')
```



4. Populate the missing values for the variable with most amount of missing data. 

```{r}
cereals%>%mutate(Sugars =replace_na(Sugars,mean(Sugars,na.rm=T)))%>%
mutate(Potass=replace_na(Potass,mean(Potass,na.rm=T)))%>%
mutate(Carbo=replace_na(Carbo,mean(Carbo,na.rm=T)))
  
```

### Descriptive Statistics
 
2. Report on the measures of centrality and spread for the calories variable of the data with at least two measures each.  


```{r}
mean(cereals$Calories)

median(cereals$Calories)
```

3. Plot histograms for the calories and protein distributions of the items. What difference(s) do you see,briefly explain how we should interpret the difference ?  

The calories are skewed more evenly than the protein distribution, where protein average begins to go down after 3.

```{r}
hist(cereals$Calories)
hist(cereals$Protein)
```


4. Create a diagram to spot outliers for the protein distribution of the items (extremely high or low in protein content). What type of items do you think they are ? Why ? 

The items with the extremely high protein content are the healthier cereals used to build muscle. 

```{r}
boxplot(cereals$Protein, main="Protein Distribution Outliers", xlab="Cereals", ylab="Proteins")
```



5. We are really interested amount of protein in items per calories. To investigate this, you need to calculate protein per calories by dividing protein amount by the calorie (protein/calories). What is the average protein per calories amount for an item.  

```{r}
cereals$avg_protein_calories = cereals$Protein/cereals$Calories
mean(cereals$avg_protein_calories)
```

